Randomized trace estimation for parameter-dependent matrices applied to spectral density approximation

### 2024-07-17 paper/re-pro-badge.tex

The code for our numerical experiments can be found on \url{https://github.com/FMatti/Rand-TRACE}. The figures and tables were generated from the commit \href{https://github.com/FMatti/Rand-TRACE/tree/75a23a4}{75a23a4} on 2024-07-11 at 06:15:48 UTC.

>>>>

The code for our numerical experiments can be found on \url{https://github.com/FMatti/Rand-TRACE}. The figures and tables were generated from the commit \href{https://github.com/FMatti/Rand-TRACE/tree/a3fd6a9}{a3fd6a9} on 2024-07-16 at 16:59:46 UTC.
